Paper 1: Vitis

### 2018-02-06 Paper-1-Vitis.Rmd
Commit from RStudio

```{r}
library(tidyverse)
library(readxl)
read_excel("R_DiLP_all_species.xlsx")
read_excel("R_DiLP_Vitis_all_added.xlsx")
```

@@

>>>>

```{r}
library(tidyverse)
library(skimr)
library(readxl)
read_excel("R_DiLP_all_species.xlsx")
excel_sheets("R_DiLP_all_species.xlsx")
read_excel("R_DiLP_Vitis_all_added.xlsx")
excel_sheets("R_DiLP_Vitis_all_added.xlsx")
```

@@

We first tested each of the variables for *Vitis acerifolia*.

```{r}
ac_all <- read_excel("R_DilP_Vitis_all_added.xlsx", sheet = "acerifolia.all.90")
str(ac_all)
ac_all$year <- as.factor(ac_all$year)
ac_all$tooth.area <- as.numeric(ac_all$tooth.area)
ac_all$tooth.area.perimeter <- as.numeric(ac_all$tooth.area.perimeter)
ac_all$tooth.area.int.perimeter <- as.numeric(ac_all$tooth.area.int.perimeter)
ac_all$average.tooth.area <- as.numeric(ac_all$average.tooth.area)
ac_all$tooth.area.blade.area <- as.numeric(ac_all$tooth.area.blade.area)
t.test(ac_all$total.teeth~ac_all$year, var.equal = TRUE)
t.test(ac_all$feret.diameter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$feret.diameter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.int.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$average.tooth.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.blade.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.int.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$perimeter.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$perimeter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$compactness~ac_all$year, var.equal = TRUE)
t.test(ac_all$shape.factor~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.blade.area~ac_all$year, var.equal = TRUE)
```
Only one variable showed a statistically significant different changes between growing seasons: tooth area to blade area (TABA).
